Comparison of approaches to using machine learning models to increase the efficiency of the global search algorithm for solving multicriterial problems

### 2024-06-30 2024/OPTIMA/OPTIMA_2024_MCO.tex
fix

\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia 
\email{a230172@unn.ru}, \email{\{konstantin.barkalov,evgeny.kozinov\}@itmm.unn.ru}, \email{vagris@unn.ru}}
%
\maketitle

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{fig1.png}
\caption{Heatmap of the function $R_ps(i)$ in the criteria space for algorithms with different machine learning models.} 
\label{fig:1}
\end{figure}

>>>>

\institute{Lobachevsky State University of Nizhni Novgorod, Nizhni Novgorod, Russia 
\email{\{konstantin.barkalov,evgeny.kozinov\}@itmm.unn.ru}, \email{vagris@unn.ru}}
%
\maketitle

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{fig1.png}
\caption{Heatmap of the function $R_{ps}(i)$ in the criteria space for algorithms with different machine learning models.} 
\label{fig:1}
\end{figure}
